Black-hole ringdown as a probe of higher-curvature gravity theories

### 2022-04-05 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: gamma gb plot

We start by showing our results for EdGB gravity.
%
In Fig.~\ref{fig:edgb_exec_sum} we show the marginalized posteriors of the
coupling constant $\ell_{\rm GB}$, for GW150914 (top panel) and GW200129
(middle panel), with and without the spin corrections to the $(2,2,0)$ QNM.
%
The bottom panel panel shows the joint posterior combining both events.
%
We see that for both events events, the $N_{\rm max} = 0$ posteriors are
characterized by a peak away from zero.
%
This does not mean that we are inferring a deviation from GR from data.
%
Recall that the deviations from GR in the ParSpec framework are controlled
by $\gamma$, which here reads,
%
\begin{equation}
    \gamma_{\rm GB} = \left(\frac{c^2 \ell_{\rm GB}}{ G M_{f}}\right)^4\,.
\end{equation}
%
As shown in Fig.~xxx, $\gamma_{\rm GB}$ does indeed have a posterior
distribution with largest support at zero, indicating consistency between data
and GR.
%
We also observe that the inclusion of the spin corrections (i.e., curves with $N_{\rm max} = 1$)
displaces the posteriors distributions towards smaller values of $\ell_{\rm GB}$.

@@

@@

We now consider dCS gravity.
%
In Fig.~\ref{fig:dCS_exec_sum} we show the marginalized posterior distribution
function of $\ell_{\rm CS}$ for both events GW150914 (top panel) and GW200129
(middle panel), with different colors distinguishing cases with and without spin corrections to
dominant $(2,2,0)$~QNM.
%
Perhaps the most salient feature of these posteriors is that they are not
peaked at $\ell_{\rm CS}$, which may mislead us to believe that we are seeing a
deviation from GR. This is not the case and the situation is that same as the
one we discussed in the previous section for EdGB gravity.
%
We verified that
%
\begin{equation}
    \gamma_{\rm CS} = \left( \frac{c^2 \ell_{\rm CS}}{G M_{f}} \right)^{4}\,,
\end{equation}
%
does indeed peak at zero indicating consistency with GR, similarly to what is shown in Fig.~\ref{} for $\gamma_{\rm GB}$.
%
We also see that in both cases that the inclusion leading-order-in-spin
correction to the mode displaces the posteriors towards smaller values of
$\ell_{\rm CS}$. This can be seen more evidently by looking at the location of
posterior peaks.
%
Finally, in the bottom panel, we show the combined result for both events.

@@

In this theory, we considered only $N_{\rm max} = 0$. We found that the
inclusion of the spin corrections yields waveforms which for $\ell_{\rm qEFT} \gtrsim 50$~km
with ringdowns portions of the larger than the inspiral-plunge part \dots
%
To avoid this issue we lowered the value of $\ell^{\rm max}_{\rm qEFT}$, but by doing so we obtained posteriors
which were essentially uniform. Thus, we do not quote any results for $N_{\rm max} = 1$.
%
Table~\ref{tab:summary_qeft} summarizes our findings for the quartic EFT of GR.

>>>>

We start by showing our results for EdGB gravity.
%
In Fig.~\ref{fig:edgb_exec_sum} we show the marginalized posteriors of the
coupling constant $\ell_{\rm GB}$, for GW150914 (top panel) and GW200129
(middle panel), with and without the spin corrections to the $(2,2,0)$ QNM.
%
The bottom panel panel shows the joint posterior combining both events.
%
We see that for both events events, the $N_{\rm max} = 0$ posteriors are
characterized by a peak away from zero.
%
This does not mean that we are inferring a deviation from GR from data.
%
Recall that the deviations from GR in the ParSpec framework are controlled
by $\gamma$, which here reads,
%
\begin{equation}
    \gamma_{\rm GB} = \left(\frac{c^2 \ell_{\rm GB}}{ G M_{f}}\right)^4\,.
    \label{eq:def_gamma_gb}
\end{equation}
%
As shown in Fig.~\ref{fig:gamma_gb}, $\gamma_{\rm GB}$ does indeed have a posterior
distribution with largest support at zero, indicating consistency between data
and GR.
%
We also observe that the inclusion of the spin corrections (i.e., curves with $N_{\rm max} = 1$)
displaces the posteriors distributions towards smaller values of $\ell_{\rm GB}$.

@@

\begin{figure}[h]
\includegraphics[width=\columnwidth]{figs/edgb_gamma.pdf}
\caption{(Color online).~Posterior distribution function on the dimensionless parameter $\gamma_{\rm GB}$,
defined in Eq.~\eqref{eq:def_gamma_gb}. We see that this parameter controls the ParSpec expansion in EdGB gravity
does have maximum support at $\gamma_{\rm GB} = 0$. This shows that our model is consistent with GR.
}
\label{fig:gamma_gb}
\end{figure}

@@

We now consider dCS gravity.
%
In Fig.~\ref{fig:dCS_exec_sum} we show the marginalized posterior distribution
function of $\ell_{\rm CS}$ for both events GW150914 (top panel) and GW200129
(middle panel), with different colors distinguishing cases with and without spin corrections to
dominant $(2,2,0)$~QNM.
%
Perhaps the most salient feature of these posteriors is that they are not
peaked at $\ell_{\rm CS}$, which may mislead us to believe that we are seeing a
deviation from GR. This is not the case and the situation is that same as the
one we discussed in the previous section for EdGB gravity.
%
We verified that
%
\begin{equation}
    \gamma_{\rm CS} = \left( \frac{c^2 \ell_{\rm CS}}{G M_{f}} \right)^{4}\,,
\end{equation}
%
does indeed peak at zero indicating consistency with GR, similarly to what is shown in Fig.~\ref{fig:gamma_gb} for $\gamma_{\rm GB}$.
%
We also see that in both cases that the inclusion leading-order-in-spin
correction to the mode displaces the posteriors towards smaller values of
$\ell_{\rm CS}$. This can be seen more evidently by looking at the location of
posterior peaks.
%
Finally, in the bottom panel, we show the combined result for both events.

@@

In this theory, we considered only $N_{\rm max} = 0$. We found that the
inclusion of the spin corrections yields waveforms which for $\ell_{\rm qEFT} \gtrsim 80$~km
for which the ringdown portions of the larger than the inspiral-plunge part \dots
%
To avoid this issue we lowered the value of $\ell^{\rm max}_{\rm qEFT}$, but by doing so we obtained posteriors
which were essentially uniform. Thus, we do not quote any results for $N_{\rm max} = 1$.
%
Table~\ref{tab:summary_qeft} summarizes our findings for the quartic EFT of GR.
%
\hs{Discuss. I don't have a good argument for why the $N_{\rm max} = 1$ are breaking down other than
we just fail to compute the waveform for $\ell_{\rm qEFT} = 80~$~km for GW150914-like masses.}
